Bird beak's elaboration and innovation

### 2022-07-15 Analysis/03-Elaboration_innovation_analysis.Rmd
added ellipses stats

```{r}
## Measuring fun
ellipse.stats <- function(data) {
    ## Get the groups list
    groups_list <- unlist(apply(matrix(c(1:(n.subsets(data)-1), rep(n.subsets(data),(n.subsets(data)-1))), ncol = 2), 1, list), recursive = FALSE)

## General measurement
super_orders_stats <- ellipse.stats(superorder_shapespace)
orders_stats <- ellipse.stats(order_shapespace)

load("../Data/Processed/tip_colours_super_orders.rda")
col <- tip_colours_super_orders
results <- super_orders_stats
## Ploting fun
ploting.stats <- function(results, col) {
    par(mfrow = c(1,3))
    ##
    plot(results[[1]], horizontal = TRUE, las = 1, xlab = "angle", ylab = "", col = col)
    plot(results[[2]], horizontal = TRUE, las = 1, xlab = "disalignment", ylab = "", yaxt = "n", col = col)
    plot(results[[3]], horizontal = TRUE, las = 1, xlab = "distance between centroids", ylab = "", yaxt = "n", col = col)
}

@@

>>>>

@@

```{r, eval = FALSE, echo = FALSE}
## Measuring fun
ellipse.stats <- function(data) {
    ## Get the groups list
    groups_list <- unlist(apply(matrix(c(1:(n.subsets(data)-1), rep(n.subsets(data),(n.subsets(data)-1))), ncol = 2), 1, list), recursive = FALSE)

## General measurement
super_orders_stats <- ellipse.stats(superorder_shapespace)
orders_stats <- ellipse.stats(order_shapespace)
suborder_stats <- ellipse.stats(suborder_shapespace)
family_stats <- ellipse.stats(family_shapespace)

ellipse_stats <- list(super_orders_stats = super_orders_stats, 
                      orders_stats = orders_stats,
                      suborder_stats = suborder_stats,
                      family_stats = family_stats)
save(ellipse_stats, file = "../Data/Processed/ellipse_stats.rda")
```

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/ellipse_stats.rda")
## Ploting fun
ploting.stats <- function(results, col) {

    col <- col[match(names(size.subsets(results[[1]])), names(col))]

    layout_matrix <- layout(matrix(1:3, nrow = 1), widths = c(4.2, 3, 3), heights = n.subsets(results[[1]])/2)
    par(mar = c(5, 10, 2, 1) + 0.1)
    plot(results[[1]], horizontal = TRUE, las = 1, xlab = "angle", ylab = "", col = col)
    par(mar = c(5, 1, 2, 1) + 0.1)
    plot(results[[2]], horizontal = TRUE, las = 1, xlab = "disalignment", ylab = "", yaxt = "n", col = col)
    par(mar = c(5, 1, 2, 1) + 0.1)
    plot(results[[3]], horizontal = TRUE, las = 1, xlab = "distance between centroids", ylab = "", yaxt = "n", col = col)
}

## Ploting fun
table.stats <- function(results, class) {
    ## Table results
    table <- cbind(summary(results[[1]])[, -c(1:3)], summary(results[[2]])[, -c(1:3)], summary(results[[3]])[, -c(1:3)])
    rownames(table) <- gsub(":phy", "", as.vector(summary(results[[1]])[,1]))
    colnames(table)[c(1,6,11)] <- c("angle", "disalignment", "distance")
    if(!missing(class)) {
        table <- cbind(class = class, table)
    }
    return(table)
}

all_results <- rbind(table.stats(ellipse_stats$super_orders_stats, class = "superorder"),
                     table.stats(ellipse_stats$orders_stats, class = "orders"),
                     table.stats(ellipse_stats$suborder_stats, class = "suborder"),
                     table.stats(ellipse_stats$family_stats, class = "family"))
knitr::kable(all_results)
```

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/tip_colours_super_orders.rda")
ploting.stats(ellipse_stats$super_orders_stats, col = tip_colours_super_orders)
```

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/tip_colours_orders.rda")
ploting.stats(ellipse_stats$orders_stats, col = tip_colours_orders)
```

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/tip_colours_passeriformes_suborder.rda")
ploting.stats(ellipse_stats$suborder_stats, col = tip_colours_passeriformes_suborder)
```

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/tip_colours_passeriformes_family.rda")
ploting.stats(ellipse_stats$family_stats, col = tip_colours_passeriformes_family)
```
